Estimating duration in the presence of misclassification

### 2024-07-29 biology-data.tex
Rob p41 clarification

Of the 738 contacts enrolled, 172 (23\%) had at least one positive test.
\Textcite{hakkiOnset} analysed the 57 contacts who tested positive for SARS-CoV-2 and had the growth phase in their viral load measured.
They excluded the remaining 115 contacts with at least one positive RT-PCR test, ATACCC did not capture the phase of the infection with increasing viral load.
This exclusion was to ensure viral load trajectories are identifiable.
I will revisit and extend their analysis in \cref{E-ATACCC}.

>>>>

Of the 738 contacts enrolled, 172 (23\%) had at least one positive test.
\Textcite{hakkiOnset} analysed the 57 contacts who tested positive for SARS-CoV-2 and had the growth phase in their viral load measured.
They excluded the remaining 115 contacts with at least one positive RT-PCR test, ATACCC did not capture the phase of the infection with increasing viral load.
This exclusion was to ensure viral load trajectories are identifiable.
The 57 contacts were divided into two groups.
The first, consisting of 32 individuals, were unvaccinated and infected with a variety of varients.
The second, consisting of the remaining 25 individuals, were vaccinated and all infected with the Delta variant.
I will revisit and extend \textcite{hakkiOnset}'s analysis in \cref{E-ATACCC}, using the same 57 contacts and groups.
The first group is more relevant to the period of interest in this thesis, and I focus on this group.
